---
title: "Homework 1"
author: "Yuxuan Wang"
date: "2023-09-23"
output: github_document
---

```{r setup, include = FALSE}
library(moderndive)
library(tidyverse)
```

# Problem 1

## Load the dataset

```{r}
data("early_january_weather")
```

* Description
  * In this dataset, variables including **`r names(early_january_weather)`**.
  * the size of the dataset is **`r nrow (early_january_weather)`** rows * **`r ncol(early_january_weather)`** cols.
  * the mean temperature is **`r mean (early_january_weather $ temp)`**.

## Scatterplot of time_hour and temp

```{r}
hour_temp_plot = ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
hour_temp_plot
```

* Description
  * From 1:00 on January 1, 2013 to 22:00 on January 15, 2013, the **temperature** continued to fluctuate up and down with **time**, in general showed an upward trend. The maximum temperature reached around 57 degrees at 11 o'clock on January 14, and then dropped rapidly. 
  * The **humidity** fluctuates between 36.82 and 100, with the highest average humidity at around 100 from January 11 to 14.

## Export scatterplot

```{r }
ggsave("scatter_plot.pdf")
```

# Problem 2

## Create a data frame

```{r}
sample_df = tibble(
  norm_samp = rnorm(10),
  vec_logical = c(norm_samp > 0),
  vec_character = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  vec_factor = factor(c("Level1", "Level2", "Level3", "Level2", "Level1", "Level2", "Level3", "Level1", "Level3", "Level1"))
)
```

## Mean of the data frame

* Mean of each variable
  * The mean of a random sample is **`r mean(pull(sample_df, norm_samp))`**.
  * The mean of a logical vector is **`r mean(pull(sample_df, vec_logical))`**.
  * The mean of a character vector is **`r mean(pull(sample_df, vec_character))`**.
  * The mean of a factor vector is **`r mean(pull(sample_df, vec_factor))`**.
* Result
  * Random sample and logical vector have the mean value, but character and factor vector do not.
  
## Convert variables

```{r, eval = FALSE}
as.numeric pull(sample_df, vec_logical)
as.numeric pull(sample_df, vec_character)
as.numeric pull(sample_df, vec_factor)
```

* Results
  * I can see the Warning messages about "vec_character" and "vec_factor", which are both **"argument is not numeric or logical: returning NA"**.
  * This help explain what happens when I try to take the mean, because "vec_character" and "vec_factor" are not numeric or logical, R cannot recognize and calculate.