---
title: "Homework 1"
author: "Yuxuan Wang"
date: "2023-09-23"
output: github_document
---

```{r setup, include = FALSE}
library(moderndive)
library(tidyverse)
```

# Problem 1

## Load the dataset

```{r}
data("early_january_weather")
```

* Description
  * In this dataset, variables including **`r names(early_january_weather)`**.
  * the size of the dataset is **`r nrow (early_january_weather)`** rows * **`r ncol(early_january_weather)`** cols.
  * the mean temperature is **`r mean (early_january_weather $ temp)`**.

## Scatterplot of time_hour and temp

```{r}
hour_temp_plot = ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
hour_temp_plot
```

* Description
  * From 1:00 on January 1, 2013 to 22:00 on January 15, 2013, the **temperature** continued to fluctuate up and down with **time**, in general showed an upward trend. The maximum temperature reached around 57 degrees at 11 o'clock on January 14, and then dropped rapidly. 
  * The **humidity** fluctuates between 36.82 and 100, with the highest average humidity at around 100 from January 11 to 14.

## Export scatterplot

```{r }
ggsave("scatter_plot.pdf")
```
